Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-30 ms.tex
updated spectra fig w/ axes labels
adding periodogram of spectra
false alarm probability for periodogram

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
\caption{The CV3 extracted spectrum shows dramatic structure.
Is this fringing?}\label{fig:cv3ExtractedSpectrum}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{labLED_ind_spec_CV3NRCN036810.pdf}
\includegraphics[width=.49\columnwidth]{labLED_spec_periodo_CV3NRCN036810.pdf}
\caption{The CV3 extracted spectrum shows large structure.
After normalizing, the periodogram shows a significant peak at a period of 37 pixels with a formal false alarm probability of $10^{-18}$.
Is this fringing?
There are also peaks at 1px and 20 px that are likely spurious.}\label{fig:cv3ExtractedSpectrum}
\end{figure}
